ODGI: understanding pangenome graphs

### 2022-01-12 manuscript/fig_extract_viz_draw_position_untangle.tex
missing the and locus in italic
fix bandage reference and add it in the main

        HG01071\#2 presents 3 copies of locus (orange), of which one contains the HERV sequence (gray in the middle of the orange).

@@

        \textbf{(f)} \textit{Bandage} layout of the C4 pangenome graph, annotated by using \textit{odgi position}. Green nodes indicate the C4 genes. The red rectangle highlights the regions where \textit{C4A} and \textit{C4B} genes differ.

>>>>

        HG01071\#2 presents 3 copies of the \textit{locus} (orange), of which one contains the HERV sequence (gray in the middle of the orange).

@@

        \textbf{(f)} \textit{Bandage}~\citep{Wick_2015} layout of the C4 pangenome graph, annotated by using \textit{odgi position}. Green nodes indicate the C4 genes. The red rectangle highlights the regions where \textit{C4A} and \textit{C4B} genes differ.
